TBD

### 2020-11-03 outputs/paper/paper.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lme4)
library(merTools)
library(readr)
library(knitr)
```
# Abstract

@@

The first few rows of the cleaned dataset can be viewed below: 
```{r}
head(tbdata)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(dplyr)
library(lme4)
library(merTools)
library(readr)
library(knitr)
```
# Abstract

@@

The first few rows of the cleaned dataset can be viewed below: 
```{r}
Table1 <- tbdata %>% 
  select(age_group, household_income_grouped, race_ethnicity, trump_biden) %>% 
  head() %>% 
  kable(align = "c",
        format = "simple",
        col.names = c("Age", "Sex", "Have Children", "Age", 
                      "Family Income", "Education Level", "Urban / Rural"),
        ) %>% 
  kable_styling(font_size = 5)
```
